Designing a Unified BBC Search\\ \vspace{2 mm}{\large Systems Design Coursework Proposal}

### 2013-07-04 proposal.tex
First draft of proposal done.

\documentclass{article}

\title{Designing a Unified BBC Search}
\subtitle{Systems Design Coursework Proposal}

@@

\section{Introduction}

This proposal is for coursework describing the design of a search application
that allows visitors to the BBC website to find anything the BBC offers
online. The focus of the design is likely around the content indexing
systems, which needs to support requirements from all areas of content
production within the BBC so as to acquire all the data required to drive
a search web application.

The scope of the coursework will be restricted to a subset of the content
areas of the BBC website so as to focus on the differing challenges, but
without the designs taking on unnecessary complexity.

\section{The Problem}

Historically, the BBC has grown its presence on the World Wide Web by
allowing individual areas within the organisation to manage their own web
pages independently. This has led to a large variation in the ways
information is stored and how that content is formatted and is accessed.

This historic, technical variation adds to the existing complexity behind
the variation in the nature of the content as the web has matured. Traditional
searches that are optimised for textual items such as news articles might
not work so well for indexing online games aimed at children. Web products
such as iPlayer offer video and audio content with very little accompanying
text.

>>>>

\documentclass[10pt,a4paper]{article}

\usepackage{fullpage}

\title{Designing a Unified BBC Search\\ \vspace{2 mm}{\large Systems Design Coursework Proposal}}
\author{Ross Fenning}

@@

\input{proposal-contents}
